%-------------------------
% Resume in Latex
% Author : Prithish Soni
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% ATS compatibility (IMPORTANT)
\input{glyphtounicode}
\pdfgentounicode=1

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% section formatting
\titleformat{\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
    \textit{#3} & {\color{dark-grey} \small #4}\\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
#1 & {\color{dark-grey}} \\
\end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge Prithish Soni} \\ \vspace{5pt}
\small
\faPhone* \texttt{(916)516-9032} $|$
\faEnvelope \texttt{soniprithish25@gmail.com} $|$
\faLinkedin \texttt{Prithish Soni} $|$
\faMapMarker* \texttt{San Francisco Bay Area} $|$
\\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{YouTube}{Aug. 2019 -- Present}
{Creator (\href{https://www.youtube.com/c/harshibar}{\myuline{@harshibar}})}{San Francisco, CA}

\resumeItemListStart
\resumeItem{Grew channel to \textbf{60k subscribers in 1.5 years}; created 80+ videos on tech and productivity}
\resumeItem{Conducted A/B testing on titles and thumbnails; \textbf{increased video impressions by 2.5M} in 3 months}
\resumeItem{Designed a Notion workflow to streamline video production and roadmapping; boosted productivity by 20\%}
\resumeItem{\textbf{Partnered with brands like Skillshare and Squarespace} to expand their outreach via sponsorships}
\resumeItem{\textbf{Highlights}: \href{https://www.youtube.com/watch?v=HhWUjp5pD0g}{\myuline{The Problem with Productivity Apps}}, \href{https://www.youtube.com/watch?v=ms4cWMsOITs}{\myuline{Obsidian App Review}}, \href{https://www.youtube.com/watch?v=PkDbkyIR44w}{\myuline{Not-So-Minimal Desk Setup}}}
\resumeItemListEnd

\resumeSubheading
{Google Verily}{Aug. 2018 -- Sept. 2019}
{Software Engineer}{San Francisco, CA}

\resumeItemListStart
\resumeItem{\textbf{Led front-end development} of a dashboard to process 50k blood samples and detect early-stage cancer}
\resumeItem{Rebuilt a Quality Control product with input from 20 cross-functional stakeholders, \textbf{saving \$1M annually}}
\resumeItem{Spearheaded product development of a new lab workflow tool, leading to a 40\% increase in efficiency}
\resumeItemListEnd

\resumeSubheading
{Amazon}{May 2017 -- Aug. 2017}
{Software Engineering Intern}{Seattle, WA}

\resumeItemListStart
\resumeItem{Worked on the Search Customer Experience Team; \textbf{received a return offer}}
\resumeItem{\textbf{Shipped a new feature to 2M+ users}}
\resumeItem{Built a back-end database service in Java}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}

\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Hyku Consulting}}{Sept. 2019 -- Mar. 2021}

\resumeItemListStart
\resumeItem{Mentored 15 students towards acceptance at top US boarding schools}
\resumeItem{Designed collaborative learning ecosystem with Trello, Miro, Google Suite}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Minimal Icon Pack}}{Sept. 2020 -- Nov. 2020}

\resumeItemListStart
\resumeItem{Designed and released 100+ minimal iOS and Android icons}
\resumeItem{Generated \$250 in sales through YouTube marketing}
\resumeItemListEnd

\resumeProjectHeading{\textbf{CommonIntern}}{Sept. 2019 -- May 2020}

\resumeItemListStart
\resumeItem{Python script to automatically apply to jobs on Glassdoor}
\resumeItem{500 stars on GitHub and featured on Hackaday}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}

\resumeSubHeadingListStart

\resumeSubheading
{Wellesley College}{Aug. 2014 -- May 2018}
{Bachelor of Arts in Computer Science and Pre-Med}{Wellesley, MA}

\resumeItemListStart
\resumeItem{\textbf{Coursework}: Data Structures, Algorithms, Databases, Computer Systems, Machine Learning}
\resumeItem{\textbf{Research}: MIT Graybiel Lab, MIT Media Lab}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}

\begin{itemize}[leftmargin=0in,label={}]
\small{\item{
\textbf{Languages}: Python, JavaScript (React.js), HTML/CSS, SQL (PostgreSQL, MySQL) \\
\textbf{Tools}: Figma, Notion, Jira, Trello, Miro, Google Analytics, GitHub, DaVinci Resolve, OBS
}}
\end{itemize}

\end{document}